A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma

### 2021-02-27 main.tex
holistic chart

empowering
(一)雙方有心理的接觸。
(二)當事人正感到焦慮或不一致(incongruence)。 
(三)治療者在治療關係中是一致的、真實的或真誠的。
(四)治療者能夠對當事人表現出無條件的正向關懷。
(五)治療者能夠同理的瞭解當事人的內在，並努力傳達「我懂你的」。
Personhood: Carl Rogers
尋找生命的意義
真誠、能深刻地善解人意
非認知性核心能力
正念止觀(在當下)
人人有自癒能力
真誠 (Genuineness/Validity/Bona Fides)
內在聲音與外在態度一致/明心見性/超越的意識狀態
(Congruence/Consistency)
共情理解(設身處地/同理心/除我執)
(Empathic Understanding of Reference/Track)
無條件關懷(不批判/頓悟)
(unconditional positive regard)
***引導出案主的無條件自我關懷 => 療癒/復原力（resilience）
諮商員的
靈性功力
治療關係
I find that when I am closest to my inner, intuitive self, when I am somehow in touch with the unknown in me, when perhaps I am in a slightly altered state of consciousness, then whatever I do seems to be full of healing. Then simply my presence is releasing and helpful\cite{Rogers1979}.
%當最接近我的內在、直覺的自我，當我與我內在那不知名的角落（the unknown in me）接觸時(靈性)，當我有一些不一樣的意識狀態時（明心見性），我發現，單純只是我的存在（presence）就能鬆綁案主而且具有療效的。
%Rogers, C. R. The Foundations of the Person-Centered Approach. Education 100, 98–107 (1979).
「診後說三句，更勝良帖十方」

@@

ground truth Y (e.x. patient's survival):\\[0.5cm]
%Y$:\\[0.3cm]
$Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n + \epsilon$
gene expression is not an independent $X_mrna$, which is correlated with other $X_body, X_stress, X_inflammation, X_ros$
There is much work to be done in investigating the functional relationships more fully.\cite{Rogers1959}
We wish the TCGA does collect holistic features from their participants in the future. % electric healthcare record, EHR, enabled in holistic way

>>>>

empowering
(一)雙方有心理的接觸。
(二)當事人正感到焦慮或不一致(incongruence)。 
(三)治療者在治療關係中是一致的、真實的或真誠的。
(四)治療者能夠對當事人表現出無條件的正向關懷。
(五)治療者能夠同理的瞭解當事人的內在，並努力傳達「我懂你的」。
Personhood: Carl Rogers
尋找生命的意義
真誠、能深刻地善解人意
非認知性核心能力
正念止觀(在當下)
人人有自癒能力
真誠 (Genuineness/Validity/Bona Fides)
內在聲音與外在態度一致/明心見性/超越的意識狀態
(Congruence/Consistency)
共情理解(設身處地/同理心/除我執)
(Empathic Understanding of Reference/Track)
無條件關懷(不批判/頓悟)
(unconditional positive regard)
***引導出案主的無條件自我關懷 => 療癒/復原力（resilience）
諮商員的
靈性功力
治療關係: patient said "I would like to talk about myself more when I visit this doctor who I trusted" % 不自覺就講出，不自主就想要聽從他的建議，不再有抗拒
I find that when I am closest to my inner, intuitive self, when I am somehow in touch with the unknown in me, when perhaps I am in a slightly altered state of consciousness, then whatever I do seems to be full of healing. Then simply my presence is releasing and helpful\cite{Rogers1979}.
%當最接近我的內在、直覺的自我，當我與我內在那不知名的角落（the unknown in me）接觸時(靈性)，當我有一些不一樣的意識狀態時（明心見性），我發現，單純只是我的存在（presence）就能鬆綁案主而且具有療效的。
%Rogers, C. R. The Foundations of the Person-Centered Approach. Education 100, 98–107 (1979).
「診後說三句，更勝良帖十方」

@@

ground truth Y (e.x. patient's survival):\\[0.5cm]
%Y$:\\[0.3cm]
$Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n + \epsilon$
gene expression is not an independent $X_mrna$, which is correlated with other $X_body, X_stress, X_inflammation, X_ros$
There is much work to be done in investigating the functional relationships more fully.\cite{Rogers1959}
We wish the TCGA does collect holistic features from their participants in the future. % electric healthcare record, EHR, enabled in holistic way
Deep Patient

We design a #holisticDental chart in our outpaitent department for Psycho-Social-Spiritual Evaluation\cite{Ling-ChengMong2021}.:
1. Emotional: stable/depression/ anxiety/ agitated/ perplexed
2. Interaction: expression disorder/ confusion/ hard to make decision/ uncooperative to dental treatment
3. Social: (disturbing living/ disturbing working/ disturbing other life aspect) by present illness
4. Function loss(subjectively): mastication/ pronunciation/ life quality/ state of mind
5. Self-expectation: lack of confidence/ low self-esteem/ social-withdrawal
6. Impact to life: financial problem/ family problem
7. Medical relationship: bad experience of dental treatment/ loss confidence to dentist/ anxious to treatment 
side-effects/ litigation experience
8. Other aspects
/no other specific issues
